---
title       : Kid's Height Predictor
subtitle    : 
author      : Maria H. Koh
job         : Class on Coursera 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, mathjax, shiny]  # {mathjax, quiz, bootstrap}
mode        : standalone # {selfcontained, draft}
knit        : slidify::knit2slides

---
## Motivation 

* Parents are very interested in their kid's height - how short or tall 
* It's very difficult to predict a child's exact adult height due to various factors. 
* However, some studies suggested that the genetics factor contributes 60%-80%. 
* And a child's height based on parental heights subjects to regression toward the mean. 
* So, we can utilize a simple formula for calculating kid's estimated adult height.

---
## How to calculate estimated kid's adult height 

1. Convert each parent's height into centimeters. For example, if mom is 5 feet 6 inches, tall, her height is 167.64 centimeters.
2. Add both parents' heights together and divide the resulting number by two. 
3. Subtract 6.35 centimeters from the result above if the child is a girl. For a boy, add 6.35 centimeters to the average of the parent's height calculated above.
4. Your child's adult height will likely fall within 10.14 centimeters of that number.

---.class #id
## Simple formula for calculation

$$\frac{FatherHeight + MotherHeight}{2} \pm 6.35$$


### Reference information
[CDC Growth Charts of the United States](http://www.cdc.gov/GrowthCharts/) are good sources of information to evaluate the growth situation of a child.
The average height of male of age 20 or older is 176.3 cm, female is 162.2 cm in the United States.
Predicted heights are usually within <strong>10.16 centimeters</strong>, taller or shorter, than actual adult height. Medical conditions and other factors can affect a child's growth.

--- 
## Kid's Height Predictor!
```{r, echo=FALSE}
library(shiny)
library(slidify)
library(slidifyLibraries)
library(XML)
```

```{r opts.label='shiny'}

slidifyUI(          
       sidebarPanel(
                HTML("<p><font size='2'>A child's height based on parental heights subjects to regression toward the mean. This calculator is base on this algorithm. Please enjoy it !</font></p>"),
                h3("kid's information"),                
                numericInput('fhinput', label="Input Father's height(cm)", value = 176.3),
                numericInput('mhinput', label="Input Mother's height(cm)", value = 162.2),
                radioButtons("gender", "Kid's gender",
                                   c("Girl" = "-1",
                                     "Boy" = "1")),
                submitButton('Calculate!'), 
                HTML("<p><font size='2'>If you don't know the exact height of your parents, you can accept the default value.</font></p>")),
        mainPanel(
                h3('Expected adult height for the kid'),
                h3('You entered'),
                paste("Father's Height(cm)"),
                verbatimTextOutput("fhoutput"),
                paste("Mother's Height(cm)"), 
                verbatimTextOutput("mhoutput"),
                paste("Kid's gender"),
                verbatimTextOutput("genderout"),
                h3('Which resulted in a prediction of'),
                verbatimTextOutput("prediction"),
                HTML("<p><font size='2'>Predicted heights are usually within <strong>10.16 centimeters</strong>, taller or shorter, than actual adult height. Medical conditions and other factors can affect a child's growth.</font></p>")                
        )
)

```
